preciseTAD: A machine learning framework for precise 3D domain boundary prediction at base-level resolution

### 2020-09-23 Manuscript/manuscript.Rmd
Polish Evaluating performance across cell lines

When evaluating performance across cell lines, we compared the strategy of training and testing binned and annotation data from the same cell line with training and testing across cell lines. To do so, we built a model using binned and annotation data from $n-1$ chromosomes of the other cell line, while maintaining same testing data from the same cell line strategy (i.e. data from the $i^{th}$ holdout chromosome). As before, this process was repeated for each holdout chromosome. To evaluate performance, we constructed receiver operating characteristic (ROC) curves composed of the average sensitivities and specificities at different cutoffs, across each holdout chromosome, and reported the corresponding average area under the curve (AUC).

>>>>

We used the same holdout chromosome strategy to evaluate a model trained in one cell line on unseen data from another cell line [@schreiber2019pitfall]. Given two cell lines, GM12878 and K562, we first evaluated the performance of cell line-specific models. That is, models trained on cell line-specific data from $n-1$ chromosomes were evaluated on the $i^{th}$ holdout chromosome data from the same cell line. Second, we evaluated models trained on cell line-specific data from $n-1$ chromosomes using the $i^{th}$ holdout chromosome data from a different cell line. That is, models trained using K562 cell line-specific data were evaluated on unseen chromosome data from GM12878 cell line. This process was repeated for each holdout chromosome. To evaluate performance, we constructed receiver operating characteristic (ROC) curves composed of the average sensitivities and specificities at different cutoffs, across each holdout chromosome, and reported the corresponding average area under the curve (AUC).
